\section{Phase 2 Main Selection}

\subsection{Phase 2 selection results}

Table \ref{tab:compare-main-req} shows the remaining tool kits. The column {\sc
Community} indicates the expected support for the tool kit.  The tool kits
qualified as \w{Partial} leave out either the GUI widgets or the 2D drawing
capability. They could still be viable in combination with one of the other
tool kits. Among the tool kits qualified as \w{Maybe} are some unconventional,
but powerful frameworks. Still, this analysis only considers the categories
\w{Yay} or \w{Partial}.

\begin{center}
    \small\sf
    \begin{tabular}{c|lccc|c|ccc}
	\hline
	\w{nr} & \w{Toolkit} & \w{C++} & \w{2D} & \w{GUI} &    & \multicolumn{3}{c}{\em\bf\sf Yay or Nay} \\
           & {\bf\sf Name}&        &        &         & \w{Community}& \w{Yay} & \w{Part} & \w{Nay} \\
           &	          &        &        &         &              &         & {\bf\sf Maybe}  &  \\
        \hline
%%%%%%%%%%%%%%%%%%  	  C++  2D  GUI  Comm  Yay   Part   Nay
%%%%%%%%%%%%%%%%%%                                  Maybe
1  &	GTK+		& 1   & 1 & 1 &  Active  & Yay &         &     \\
2  &	Qt	      	& 1   & 1 & 1 &  Active  & Yay &         &     \\
3  &	WxWidgets 	& 1   & 1 & 1 &  Active  & Yay &         &     \\
4  &	FLTK      	& 1   & 1 & 1 &  Active  & Yay &         &     \\
\hline
8  &	Cairo     	& 1   & 1 & 0 &  Large  &     & Partial &     \\
9  &	OpenGL 	  	& 1   & 1 & 0 &  Large  &     & Partial &     \\
10 &	SDL			& 1   & 1 & 0 &         &     & Partial &     \\\hline
\hline
5  &	JUCE      	& 1   & 1 & 1 &  Small  &     & Maybe   &     \\
6  &	CEGUI     	& 1   & 1 & 1 &  Active &     & Maybe   &     \\
7  &	Gled		& 1   & 1 & 1 &  Small  &     & Maybe   &     \\
11 &	Mozilla A.F.  	& 1   & 1 & 1 &  Large  &     & Web-oriented   &     \\\hline
12 &	Tk	        & 0.5 & 1 & 1 &  Large  &     &         & Nay \\
13 &	fpGUI     	& 0   &   &   &         &     &         & Nay \\
14 &	GDK       	& 1   & 1 & 0 &  Large  &     &         & Nay \\
\hline
    \end{tabular}
    \captionof{table}{Selected tools against must have product/project requirements}
	\label{tab:compare-main-req}
\end{center}

\subsection{Phase 2 selection analysis}

\paragraph{Tool kits included} The tool kits 1 through 4 satisfy the
requirements.  

The tool kits 8 and 9 satisfy all but one requirement (the GUI) but could still
function if they add sufficient function to a GUI oriented toolkit. 

\paragraph{Tool kits excluded} Tool kit 10 ({\sf SDL}) is not clear on the
supporting community, but does seem to have a following.  The comparison from
\w{WxWidgets} (\cite{wxwidget:comparison}) mentions {\sf SDL} as a viable
addition to \w{WxWidgets}, but oriented towards gaming. The tool kits 12
through 13 do not satisfy the requirements fully, and tool kit 14 (GDK) is low
level and incorporated in {\sf GTK+}.  The Mozilla Application Framework ({\sf
M.A.F.}) is oriented towards the web. The deciding feature is that {\sf MAF}
contains a sub selection of the regular GUI widgets geared towards html and
css.

For \w{fpGUI}, \w{sdl} and \w{Gled} the community activity is not clear from
the home website, so the community is left out in table. The system \w{juce} is
a one man project and aimed at multimedia and gaming.  \w{cegui} is a small
community of developers specifically aimed at gaming, not graphical user
interface.  \w{Gled} is a framework that stems from scientific work and
features the easy distribution of nodes across threads, processes and machines.
See \cite{greed:gled} for a discussion of the scientific goals of the \w{Greed}
project.

\paragraph{Next phase} will contain toolkits $1, 2, 3$ and 4: {\sf GTK+, Qt,
WxWidgets, FLTK} with possible additions of OpenGL or Cairo. 

