\section{Problem domain}
\subsection{Description}

The customer's request is to build a graphical chip editor for Network on chip
designs that uses existing C++ program to interface with and that runs on all
defined platforms: Linux, ms Windows and Mac. This implies part of the solution
is a user interface tool that works from graphical representation of chip
networks. This document is the result of gathering information and analysing
existing user interface tools that we could use for this purpose. Addiditonally
the customer has specified some qualitative requirements like maintainability
and installability.

\subsection{Requirements for the approach}

The number of available user interface toolkits is large.  Moreover the number
of features each toolkit has, is large. This warrants careful consideration of
toolkits where we start from the project's requirements and use the team's
preference to break any ties.  The primary goal is that the UI tool suffices:
it does not have to be perfect.

\section{Search}

\subsection{Search apporach}

Normally one searches literature for information on subjects in domain
analysis.  For toolkits this may not be the most efficient or effective way of
finding the best toolkit. The problem with literature is that it is constantly
behind on the current state of affairs. Even though information on the internet
in general is less reliable than literature generally is, in this case it forms
a better basis to find a more complete list of toolkits. 

Using the en.wikipedia as entrance and fanning out through the links wikipedia
provides we were able to determine a list of user interface toolkits that in
practice is sufficient for our goal. The dates on the sites provide information
on how actual the data is. Crossreferencing sites gives confidence in the
correctness of the information. The next section lays out the criteria we used
to select toolkits.

\subsection{Selection criteria}

Table \ref{tab:appl-requirements} contains a list of the main requirements for
the design tool. These requirements generate criteria which we can use to find
the most appropriate toolkits available.

Table \ref{tab:team-competence-req} shows a list of the team's preferences.
Any ties\footnote{toolkits with equal qualification regarding requirements} can
be broken using the team members preferences. Table
\ref{tab:itool-requirements} shows the implications of the requirements
resulting in specific user interface requirements.

The next section shows what the steps we followed and what the results were.

\subsection{Selection process}

Table \ref{tab:discarded-toolkits} shows the first wave of packages that did
not make the comparis due to not satisfying one of the important requirements
(being free software, running on the defined platforms).

Table \ref{tab:compare-main-req} shows the result of the second wave of
selection. These packages satisfy all main requirements and need further
selection. 

\subsection{Result}

We reduced the list of the complete set of user interface toolkits (see
\ref{tab:discarded-toolkits} and \ref{tab:compare-main-req}) to 3
candidate toolkits: GTK+, Qt and WxWidget. In terms of main requirements they
are equal. Remaining task is to determine the best of these alternatives in
terms of detailed requirements. 

\todo{Final compare}.

\section{Recommendation}

We recommend the team to choose toolkit <GTK+, Qt, WxWidget>\todo{choice} on the basis
of <what is the main reason>\todo{motive}.

\subsection{Motivation}

We have chosen\todo{Expanded motive}.
