\section{Search and Selection}

\subsection{Search approach motivation}

Normally one searches literature for information on science subjects.  For tool
kits this may not be the most efficient or effective way of finding current
tool kits. The problem with literature is that it is constantly behind on the
current state of affairs. Even though information on the internet is generally
less reliable than literature is, in this case it forms a better basis to find
a more complete list of tool kits. Literature does supplement what we find on
the internet.

This analysis is able to determine a list of user interface tool kits starting
from en.widipedia and fanning out through the links wikipedia provides and a
search engine. The dates on the sites provide information on how actual the
data is. Cross referencing sites gives confidence in the correctness of the
information. The next section lays out the criteria we used to select tool
kits.

\subsection{Selection criteria}

Table \ref{tab:appl-requirements} on page~\pageref{tab:appl-requirements}
contains a list of the main requirements for the design tool. These
requirements generate criteria that we can use to find the most appropriate
tool kits available.  Table \ref{tab:team-competence-req} on
page~\pageref{tab:team-competence-req} shows a list of the team's preferences.
Table \ref{tab:uitool-requirements} on page~\pageref{tab:uitool-requirements}
shows the implications of the requirements resulting in specific user interface
requirements. The next section shows what steps I followed and what the
results were.

\subsection{Phase 1: Primary deselection}

The first phase deselects tool kits that do not suffice one
of the important requirements.  Table \ref{tab:discarded-toolkits} on
page~\pageref{tab:discarded-toolkits} shows the tool kits that were deselected
and why.

\subsection{Phase 2: Secondary deselection}

The remaining tool kits were examined in more detail. Each one of these tool
kits finds a summarized description in appendix~\ref{sec:phase2-listing}.  This
results in rating the tool kits according to the main characteristics required
in Table~\ref{tab:compare-main-req} on page~\pageref{tab:compare-main-req}.

Analysis of the results leads to accept the first four for definite 
comparison in the last phase. These tool kits have all necessary
characteristics required. The next three tool kits represent
2D tool kits that could be used in conjunction with the first four.

\subsection{Phase 3: Final selection}

This phase concerns the tool kits : \w{gtk+}, \w{qt}, \w{wxwidgets} and
\w{fltk}. See appendix~\ref{sec:phase2-listing} for a summary of each tool kit
and appendix~\ref{sec:final-listing} for a more detailed description.  Each of
these tool kits satisfies all requirements either autonomously or in
combination with other tool kits. In terms of requirement based selection, the
search is finished.

The next section documents the considertions and the resulting recommendation.

