\todo[inline]{
beschrijving van het opgeleverde eindproduct, plusminus 15 pagina’s}
\begin{tcolorbox}[colback=green!30]
  in progress - stefan
\end{tcolorbox}

\section{Setup}

\section{Project}

\section{Tool}

\section{Remarks}
\begin{itemize}
\item	bugs
\begin{enumerate}
\item	No model modified flag when packet changed
\item	Packet dialog not cleared on new/open network
\item	Model modified flag set after new when canvas was not clear
\item	Invalid maximized main window restore from setup (Qt Bug)
\item	Group select has not always key focus (e.g. pressing delete has no effect)
\item	Clicking new if canvas is not clear aborts application under Linux.
\item	Model setup not restored on model open.
\item With composite on canvas and click new then dialog save first $+$ no does not
work
\item Sometimes a composite its mouse area becomes inactive. (start with a clean
canvas , add a composite in the library and drag one on the canvas. Save new
model and click new or open). This only occurs with new (nameless) networks,
adding a composite is probably not handled well in the xMAS networks list and
therefore do only exists on the canvas.
\item	Several memory leaks
\end{enumerate}

\item	fixes
\begin{enumerate}
\item	Grid snap on port center instead of component body left top
\item	Grid snap when drag a group of items
\item	Qt save as dialog not available in version 5.4.0
\item QML uses non blocking calls, cannot use yes/no dialogs feedback in a
proper way.
\item Use of destroy dialog to quit application from QML dialog to prevent
Windows warning (Qt bug).
\item	Tooltip for composites in library to show alias or filename
\item Allow entering source expression when not connected (xmas parser)
\item New page is now done by select all and delete, instead destroy page and
create new page.
\item Remove qml convert logic in network.cpp, instead send a add component
request to the canvas by its name and type. Signal the update to component.cpp
which already does the request to xMAS for the other properties like x,y,… This
to avoid duplicate conversion and checks.
\end{enumerate}
\item	features
\begin{enumerate}
\item	(x,y) anchor list to draw a channel via these points
\item	Pathfinder algorithm for channels (e.g. A*)
\item	Canvas scroll while drag items
\item	Canvas copy-cut-paste
\item	Canvas undo-redo
\item	Canvas rotate group selection
\item	Redirect standard output to the plug-in consoles
\item	Plug-in parameters change read-only to editable list
\item	Replace auto plug-in load from fixed folder to add/remove
\item	Model export
\item	Parametric composite
\item	Packet editor as editable key/value list
\item	Plug-in tools add progress value.
\item	Plug-in tools add stop process. 
\item	Deadlock checker with plug-in interface
\item	Plug-in structured text for “in model” feedback
\item Channel rewire via clicking a connected port. (no you need to delete and
create new channel)
\item	Multi page model editor
\item	Open composite sub network in main model (e.g. on a new page)
\item	Application help
\item A platform dependent binaries package of the Qt project so that user can
install the application without having Qt or other tools installed.
\end{enumerate}
\end{itemize}


%%\newpage

